Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-20 Ben_Manuscripts/Paper1/Outline.tex
working on paper

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.
  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
   % \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

@@

  In order to construct an initial configuration which gives reliable 
  trends, we need to understand the composition of layers, how far apart
  to stack the layers, and how to orient them with respect to each other.
  \begin{itemize}
  	\item To verify our choices for each parameter, we compare our calculations
	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
	scattering (WAXS), and ionic conductivity measurements.
  \end{itemize}

  To discern the composition of the monomer layers, we ran simulations of 
  systems created with 4 - 8 monomers per layer.
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.
	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns. The 4 monomer system was run for 200 ns. 5 and 6 have a lot of data. 7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing. But I'll extend them just to be thorough.

	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item We verified that the system stays partitioned into layers by plotting 
	pair correlation functions calculated between aromatic rings along the length
	of the pores (Fig~\ref{fig:zdf}).
        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
	%BJC: okay, need to run some calculations here.
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

@@

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the $q_z$ value of
	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom$^-1$. The real space separation 
	corresponds to 4.5 \angstrom~ which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
        %MRS: the basin is with respect to. 
	%BJC: added sentence to beginning of paragraph
        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
        %\item We will refer to this system as
        %MRS: maybe Basin O and Basin C for open and closed?
	%BJC: That works but 'capital oh' might get confused with zero
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
        %MRS: see above for clarifying ``basins''.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.  %MRS: remind people why.
  \end{itemize}

@@

  %MRS: by this point, it's not clear that the directions at the
  %beginning have clearly laid out what is being done. You want all of
  %the logic you are going to use to be laid out by the introduction,
  %so that only the results are left to reveal.  Fit what you are doing 
  %in the logic pattern you lay out (which may sometimes require adjusting the logic a bit)

  We varied the initial relative interlayer orientation between sandwiched and 
  parallel-displaced based on our knowledge of the stability of the two
  pi-stacking modes.
  \begin{itemize}
  	\item We generated simulated X-ray diffraction patterns using simulation trajectories from the highly
	restrained initial configurations created during equilibration
	\item The simulated patterns establish a difference between the two stacking 
	modes (Figure~\ref{fig:XRDrestrained}).
	\item In each pattern, R-alkanes is present at a distance of $\approx
	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
  	\item R-$\pi$ is also present in each pattern, although it appears to 
	intersect R-alkanes because the spacing between aromatic rings is 
	similar to the alkane chain packing.
        %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
	%BJC: okay added some more specific language
	\item The difference in aromatic ring spacing between experiment and
	simulation is likely a result of the inability of GAFF to properly handle
	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
	\item The sandwiched configuration shows R-spots in the expected location.
	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
	\item The parallel displaced configuration contains two lines of high 
	intensity with maximum intensity occurring where they intersect the alkane
	chain region due to constructive interference between the two features.
	\item The lines are located where one would expect to see R-helix and, 
	perhaps coincidentally, the intersection with R-alkanes occurs where one 
	would expect to see R-spots.
	%BJC: might save the following sentence for equilibrium trajectories
	\item As the simulation is progressed, the full line begins to fade 
	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
	where R-helix exists.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.475\textwidth}
		\hspace{-1.2cm}
		\centering
		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
		\caption{}\label{fig:rzplayeredrestrained}
	\end{subfigure}
	\begin{subfigure}{0.475\textwidth}
		\hspace{-1.2cm}
		\centering
		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
		\caption{}\label{fig:rzoffsetrestrained}
	\end{subfigure}
	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
	with restraints placed on aromatic carbons shows all major features
	present in experimental WAXS. Near solid lines at constant z are a result of 
	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
	restrained parallel displaced configuration may also contain all
	major experimental WAXS features. One can argue that R-spots is not present
	but it is difficult to distinguish because of its intersection with the solid
	R-helix line. 
        %MRS: Longer simulations are necessary to determine which structure
	% is the best match to experiment
        %MRS: we probably want to avoid saying this (above) if we can.
}\label{fig:XRDrestrained}
  \end{figure}

  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.  Something to think about.
  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
  %MRS: make sure the figures are comparable.  Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the sandwiched configuration in Basin A.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards Basin B.
	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as the disordered system. 
%BJC: omit and call it basin B
%MRS or just be consistent from the beginning.  Or call Basins O and D          
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
	%BJC: maybe break into a separate paragraph starting here
	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated upon full spherical integration of the 3D 
	structure factor. However, the same information can be extracted by measuring 
	the pore spacing as described earlier.
	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom~.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
	R-helix, R-$\pi$ and R-spots are not present.
  \end{itemize}

@@

  The spots that appear in the simulated XRD pattern of the sandwiched
  conformation are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails are mostly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:angle_distribution}).
	\item We reason that monomer tails stacked closely in the sandwiched conformation
	are forced to splay apart and pack in between in each other which creates a
	nearly hexagonal array of packed tails. 
        %MRS: hmm.  and this doens't happen in parallel displaced? I thought it did.
        %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
	%BJC: There aren't spots in parallel displaced and the distribution does not have the spikes that the sandwiched configuration does. At this point in the paper, I've tried to say that parallel displaced configuration is not consistent with experiment and I focus the rest of the paper on the sandwiched configuration
  \end{itemize}

>>>>

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.

  % The following methodology is taken from the 2014 Feng et al. paper where
  % WAXS is reported. The data we are using comes from the 2016 paper which 
  % I assume used the same set up but I will need to verify this with Xunda
  % before this gets sent out. The SAXS is the same as shown in the 2016 paper
  % however I will likely reproduce it with matplotlib 
  Experimental wide angle X-ray scattering measurements were performed using a 
  Rigaku 007 HF+ instrument with a rotating anode Cu K$\alpha$ X-ray source
  ($\lambda$~= 1.542 \angstrom~) and a 2-D Saturn 994+ CCD detector. The 
  calibrations of the resultant 2-D WAXS patterns were done by using a 
  silicon powder standard (d-spacing of 3.1355 \angstrom~). 2-D SAXS scattering
  patterns were integrated into 1-D plots of scattering intensity (I) versus
  q, where q = 4$\pi$sin($\theta$)/$\lambda$ and the scattering angles is
  2$\theta$. The data shown is reproduced from data collected elsewhere~\ref{feng_scalable_2014}.

  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
   % \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

@@

  %In order to construct an initial configuration which gives reliable 
  %trends, we need to understand the composition of layers, how far apart
  %to stack the layers, and how to orient them with respect to each other.
  %\begin{itemize}
  %	\item To verify our choices for each parameter, we compare our calculations
  %	to experimental small angle X-ray scattering (SAXS), wide angle X-ray
  %	scattering (WAXS), and ionic conductivity measurements.
  %\end{itemize}

  We will now address the questions raised in the introduction in the order
  that they were asked.

  To answer (1), we verified that the system stays partitioned into layers by
  plotting the pair correlation function calculated between aromatic rings along
  the length of the pores (Fig~\ref{fig:zdf}).
  \begin{itemize}
	\item Period of fluctuation (layer spacing)
        \item Magnitude of fluctuations
	\item Comment on difference between offset/layered, number of monomers per layer
  \end{itemize}

  To discern the composition of the monomer layers, addressing (2), we ran 
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.
	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns. The 4 monomer system was run for 200 ns. 5 and 6 have a lot of data. 7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing. But I'll extend them just to be thorough.
	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

@@

  To answer question (3) we require high resolution experimental evidence which we 
  can match to our simulations. Experimental WAXS measurements encode all structural
  details and we would like to match them as well as possible. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the $q_z$ value of
	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom$^-1$. The real space separation 
	corresponds to 4.5 \angstrom~ which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  We were inspired to ask question (4) when we observed that the initial distance
  between layers can influence the approach towards equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
	open pore structure.
        \item We will refer to this large set of configurations, with an open pore, as 
        Basin OP (open pore) (Figure~\ref{fig:abasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.
  \end{itemize}

@@

  % BJC: This paragraph needs to change since, upon inspection, it appears that the 
  % offset configuration is correct. So it needs to shine a more positive light on offset
  % BJC: I think it can be deleted
  %We varied the initial relative interlayer orientation between sandwiched and 
  %parallel-displaced based on our knowledge of the stability of the two
  %pi-stacking modes.
  %\begin{itemize}
  %	\item We generated simulated X-ray diffraction patterns using simulation 
  %      trajectories from the highly restrained initial configurations created during 
  %	equilibration
  %	\item The simulated patterns establish a difference between the two stacking 
  %	modes (Figure~\ref{fig:XRDrestrained}).
  %	\item In each pattern, R-alkanes is present at a distance of $\approx
  %	1.5$ \angstrom$^-1$ (4.2 \angstrom~ in real space).
  %	\item R-$\pi$ is also present in each pattern, although it appears to 
  %	intersect R-alkanes because the spacing between aromatic rings is 
  %	similar to the alkane chain packing.
  %     %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
  %	%BJC: okay added some more specific language
  %	\item The difference in aromatic ring spacing between experiment and
  %	simulation is likely a result of the inability of GAFF to properly handle
  %	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
  %	\item The sandwiched configuration shows R-spots in the expected location.
  %	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
  %	\item The parallel displaced configuration contains two lines of high 
  %	intensity with maximum intensity occurring where they intersect the alkane
  %	chain region due to constructive interference between the two features.
  %	\item The lines are located where one would expect to see R-helix and, 
  %	perhaps coincidentally, the intersection with R-alkanes occurs where one 
  %	would expect to see R-spots.
	%BJC: might save the following sentence for equilibrium trajectories
  %	\item As the simulation is progressed, the full line begins to fade 
  %	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
  %	where R-helix exists.
  %\end{itemize}

  %\begin{figure}[!ht]
  %	\centering
  %	\begin{subfigure}{0.475\textwidth}
  %		\hspace{-1.2cm}
  %		\centering
  %		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
  %		\caption{}\label{fig:rzplayeredrestrained}
  %	\end{subfigure}
  %	\begin{subfigure}{0.475\textwidth}
  %		\hspace{-1.2cm}
  %		\centering
  %		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
  %		\caption{}\label{fig:rzoffsetrestrained}
  %	\end{subfigure}
  %	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
  %	with restraints placed on aromatic carbons shows all major features
  %	present in experimental WAXS. Near solid lines at constant z are a result of 
  %	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
  %	restrained parallel displaced configuration may also contain all
  %	major experimental WAXS features. One can argue that R-spots is not present
  %	but it is difficult to distinguish because of its intersection with the solid
  %	R-helix line. 
        %MRS: Longer simulations are necessary to determine which structure
	% is the best match to experiment
        %MRS: we probably want to avoid saying this (above) if we can.
%}\label{fig:XRDrestrained}
%  \end{figure}

  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.  Something to think about.
  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
  %MRS: make sure the figures are comparable.  Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the offset configuration in the OP basin.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
%BJC: omit and call it basin B
%MRS or just be consistent from the beginning.  Or call Basins O and D          
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
	%BJC: maybe break into a separate paragraph starting here
	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated upon full spherical integration of the 3D 
	structure factor. However, the same information can be extracted by measuring 
	the pore spacing as described earlier.
	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom~.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
	R-helix, R-$\pi$ and R-spots are not present.
  \end{itemize}

@@

  The spots that appear in the simulated XRD pattern of the sandwiched
  conformation are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (Figure~\ref{fig:tilt}). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails are mostly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:angle_distribution}).
	\item We reason that monomer tails stacked closely in the sandwiched conformation
	are forced to splay apart and pack in between in each other which creates a
	nearly hexagonal array of packed tails. 
        %MRS: hmm.  and this doens't happen in parallel displaced? I thought it did.
        %thought it did before. Would be good to explore the equivalent of figure 9 to this, because that comparison would make it clearer what the structural reason is for the R-spots.
  \end{itemize}
